A user-extensible and adaptable parser architecture

### 2008-05-29 papers/sgai-2008/paper.tex
Use varioref for references; still using the same format for distant references,     switched to the better format provided by varioref for close references. Removed tocbibind: no point in using it in this document, and it gives a smaller     bibliography. Minor other changes.

% Useful stuff for math mode.
\usepackage{amstext}
% The name of the program, so I only have to change it in one place.
\newcommand{\parsername}{\PLP{}}
\newcommand{\parsernames}{\PLP{}'s}
% Include images
\usepackage[final]{graphicx}
\renewcommand{\refname}{Bibliography}
% Add the bibliography into the table of contents.
\usepackage[section,numbib]{tocbibind}
% Provides commands to distinguish between pdf and dvi output.
\usepackage{ifpdf}
\usepackage{url}

@@

% Extra packages recommended by Springer.
\usepackage{mathptmx}
\usepackage{helvet}
\usepackage{courier}
\usepackage{makeidx}
\usepackage{multicol}
\usepackage{cite}

@@

% Replacement for \ref{}, adds the page number too.
\newcommand{\refwithpage}[1]{%
    \empty{}\ref{#1} [p.~\pageref{#1}]%
}
% section references, automatically add \textsection
\newcommand{\sectionref}[1]{%
    \textsection{}\refwithpage{#1}%
}

@@

XXX USE citeref AND A REFERENCE PACKAGE WHICH PUTS CLEVER PAGE NUMBERS ON
REFERENCES\@.

@@

An important property of a parser is how execution time scales relative to
input size: does it scale linearly, polynomially, or exponentially?
Figure~\refwithpage{execution time vs file size vs number of lines graph}
shows the execution time in seconds, file size in MB, and tens of thousands
of log lines per log file.  All three lines run roughly in parallel, giving
a visual impression that the algorithm scales linearly with input size.
This impression is borne out by fig.~\refwithpage{execution time vs file
size vs number lines factor} which plots the ratio of file size vs
execution time, and ratio of number of log lines vs execution time (higher
is better in both cases).  As the reader can see the ratios are quite
tightly banded across the graph, showing that the algorithm scales
linearly: the much larger log files between points 60 and 70 on the X axis
in fig.~\refwithpage{execution time vs file size vs number of lines graph}
actually cause the ratio to increase (i.e.\ improve), rather than decrease.
The strange behaviour where larger log files are parsed more efficiently is
explained in \sectionref{Why are there dips in the graphs?}.

>>>>

% Useful stuff for math mode.
\usepackage{amstext}
% The name of the program, so I only have to change it in one place.
\newcommand{\parsername}{\PLP{}}
\newcommand{\parsernames}{\PLP{}'s}
% Include images
\usepackage[final]{graphicx}
%\renewcommand{\refname}{Bibliography}
% Add the bibliography into the table of contents.
%\usepackage[section,numbib]{tocbibind}
% Provides commands to distinguish between pdf and dvi output.
\usepackage{ifpdf}
\usepackage{url}

@@

% Extra packages recommended by Springer.
\usepackage{mathptmx}
\usepackage{helvet}
\usepackage{courier}
\usepackage{makeidx}
\usepackage{multicol}

% Nicer citation lists - smaller spaces.
\usepackage{cite}
% Adds page numbers to bibliography entries, showing where they were cited.
% Breaks when cite is used.
% \usepackage{citeref}
% Check for unused references.
% \usepackage{refcheck}
\usepackage{varioref}
% Warnings rather than errors when references cross page boundaries.
\vrefwarning{}
% Errors when loops are encountered
\vrefshowerrors{}
% Show all the files/packages loaded.
%\listfiles

@@

% Replacement for \ref{}, adds the page number too.
\newcommand{\refwithpage}[1]{%
    %\empty{}\ref{#1} [p.~\pageref{#1}]%
    \empty{}\vref{#1}%
}
% Shorten the text used for references with page numbers.
\renewcommand{\reftextfaraway}[1]{%
    [p.~\pageref{#1}]%
}
% section references, automatically add \textsection
\newcommand{\sectionref}[1]{%
    %\textsection{}\refwithpage{#1}%
    \textsection{}\vref*{#1}%
}

@@

@@

An important property of a parser is how execution time scales relative to
input size: does it scale linearly, polynomially, or exponentially?
Figure~\refwithpage{execution time vs file size vs number of lines graph}
shows the execution time in seconds, file size in MB, and tens of thousands
of log lines per log file.  All three lines run roughly in parallel, giving
a visual impression that the algorithm scales linearly with input size.
This impression is borne out by fig.~\refwithpage{execution time vs file
size vs number lines factor} which plots the ratio of file size vs
execution time, and ratio of number of log lines vs execution time (higher
is better in both cases).  As the reader can see the ratios are quite
tightly banded across the graph, showing that the algorithm scales
linearly: the much larger log files at points 62--68 on the X axis in
fig.~\refwithpage{execution time vs file size vs number of lines graph}
actually cause the ratio to increase (i.e.\ improve), rather than decrease.
The strange behaviour where larger log files are parsed more efficiently is
explained in \sectionref{Why are there dips in the graphs?}.
